---
title: "Field plots to point data"
author: "Anna Talucci"
date: "6/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Overview

Create spatial points data  fram  for plots that burned from 2001 to present. Point data will be used  to extract  dnbr and RdNBR values from satellite imagery of of burn severity  calculations.

# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(stringr)
library(sp) # spatial data
library(rgdal) # geospatial data
library(raster) # deals with rasters
library(ggplot2)
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(latticeExtra)
library(sf)
```

# Functions
function to remove rowswith NA in Lat/long  column
```{r}
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
```


# Field Data Org

```{r}
site_info = read.csv("../data/field/site_info_2018-2019.csv")
```


```{r}
head(site_info)
```

# Subset field data by transect

## Create a unique ID for each point
```{r}
site_info2 = site_info %>% mutate(ID =  paste(site, burn_year, transect, plot, sep = '_')) %>%  
  dplyr::select(ID, longitude:elevation, region:plot, slope:aspect)

site_info2
```


Select by burn year
```{r}
unique(site_info2$burn_year)
```


```{r}
site_info2 %>% filter(burn_year >= 2001) 
```

Burn years include 2001, 2002, 2003, 2010, 2015

## Create separte dataframe for each fire year

```{r}
burn2001 = site_info2 %>% filter(burn_year == 2001) 
burn2001
```

```{r}
burn2002 = site_info2 %>% filter(burn_year == 2002) 
burn2002 = completeFun(burn2002, c("longitude", "latitude"))
burn2002
```

```{r}
burn2003 = site_info2 %>% filter(burn_year == 2003) 
burn2003
```

```{r}
burn2010 = site_info2 %>% filter(burn_year == 2010) 
burn2010
```


```{r}
burn2015 = site_info2 %>% filter(burn_year == 2015) 
burn2015 = completeFun(burn2015, c("longitude", "latitude"))
burn2015
```
# Spatial data

## Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 
+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 "
```

# Data frame to  points (spatial dataframe)

## Burn2001

Define coordinates and generate spatial point data frame with attributes

```{r}
coords_burn2001 = cbind(burn2001$longitude, burn2001$latitude)
burn2001_pt <- SpatialPointsDataFrame(coords_burn2001, proj4string = CRS(wgs_proj), data = burn2001)
```

Transform to Equal area projection for buffer
```{r}
burn2001_pt_ee <- spTransform(burn2001_pt, CRS(ee_russia))
```

```{r}
burn2001_pt_ee
```

Generate a spatial buffer
```{r}
burn2001_pt_ee_30m = gBuffer(burn2001_pt_ee, width = 30, capStyle="SQUARE", joinStyle="ROUND")
```

Spatial transform Buffer back to WGS

```{r}
burn2001_buff_30m <- spTransform(burn2001_pt_ee_30m, CRS(wgs_proj))
```

Transform from sp to sf

```{r}
burn2001_pt_sf = st_as_sf(burn2001_pt)
burn2001_buff_30m_sf = st_as_sf(burn2001_buff_30m)
```

```{r}
burn2001_pt_sf
burn2001_buff_30m_sf
```


Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(burn2001_pt_sf, "../outputs/point_data/burn2001_wgs84.shp", driver="ESRI Shapefile") 
```

```{r eval=FALSE, include=FALSE}
st_write(burn2001_buff_30m_sf, "../outputs/point_data/burn2001_wgs84_30m.shp", driver="ESRI Shapefile") 
```

## Burn2002

Define coordinates and generate spatial point data frame with attributes

```{r}
coords_burn2002 = cbind(burn2002$longitude, burn2002$latitude)
burn2002_pt <- SpatialPointsDataFrame(coords_burn2002, proj4string = CRS(wgs_proj), data = burn2002)
```

Transform from sp to sf

```{r}
burn2002_pt_sf = st_as_sf(burn2002_pt)
```

Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(burn2002_pt_sf, "../outputs/point_data/burn2002_wgs84.shp", driver="ESRI Shapefile") 
```

## Burn2003

Define coordinates and generate spatial point data frame with attributes

```{r}
coords_burn2003 = cbind(burn2003$longitude, burn2003$latitude)
burn2003_pt <- SpatialPointsDataFrame(coords_burn2003, proj4string = CRS(wgs_proj), data = burn2003)
```

Transform from sp to sf

```{r}
burn2003_pt_sf = st_as_sf(burn2003_pt)
```

Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(burn2003_pt_sf, "../outputs/point_data/burn2003_wgs84.shp", driver="ESRI Shapefile") 
```

## Burn2010

Define coordinates and generate spatial point data frame with attributes

```{r}
coords_burn2010 = cbind(burn2010$longitude, burn2010$latitude)
burn2010_pt <- SpatialPointsDataFrame(coords_burn2010, proj4string = CRS(wgs_proj), data = burn2010)
```

Transform from sp to sf

```{r}
burn2010_pt_sf = st_as_sf(burn2010_pt)
```

Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(burn2010_pt_sf, "../outputs/point_data/burn2010_wgs84.shp", driver="ESRI Shapefile") 
```

## Burn2015

Define coordinates and generate spatial point data frame with attributes

```{r}
coords_burn2015 = cbind(burn2015$longitude, burn2015$latitude)
burn2015_pt <- SpatialPointsDataFrame(coords_burn2015, proj4string = CRS(wgs_proj), data = burn2015)
```

Transform from sp to sf

```{r}
burn2015_pt_sf = st_as_sf(burn2015_pt)
```

Write to shapefile

```{r eval=FALSE, include=FALSE}
st_write(burn2015_pt_sf, "../outputs/point_data/burn2015_wgs84.shp", driver="ESRI Shapefile") 
```